%latex.default(tex, file = file, caption = caption, rowname = NULL,     booktabs = TRUE, longtable = TRUE, lines.page = nrow(tex),     here = TRUE, col.just = col.just)%
\setlongtables\begin{longtable}{p{60mm}p{10mm}p{5mm}p{5mm}p{5mm}p{5mm}p{5mm}p{5mm}}\caption{Fidelity table for 6 partitions. Statistics threshold: 0.5. Relevees per partition: 1:25, 2:13, 3:6, 4:6, 5:15, 6:22.  } \tabularnewline
\toprule
\multicolumn{1}{c}{Taxon}&\multicolumn{1}{c}{Layer}&\multicolumn{1}{c}{1}&\multicolumn{1}{c}{2}&\multicolumn{1}{c}{3}&\multicolumn{1}{c}{4}&\multicolumn{1}{c}{5}&\multicolumn{1}{c}{6}\tabularnewline
\midrule
\endfirsthead\caption[]{\em (continued)} \tabularnewline
\midrule
\multicolumn{1}{c}{Taxon}&\multicolumn{1}{c}{Layer}&\multicolumn{1}{c}{1}&\multicolumn{1}{c}{2}&\multicolumn{1}{c}{3}&\multicolumn{1}{c}{4}&\multicolumn{1}{c}{5}&\multicolumn{1}{c}{6}\tabularnewline
\midrule
\endhead
\midrule
\endfoot
\label{tex}
&&&&&&&\tabularnewline
\textbf{typical for 1}&&&&&&&\tabularnewline
Bryum schleicheri s.lat.&ml&\multicolumn{1}{|l|}{32***}&.&.&.&.&.\tabularnewline
&&&&&&&\tabularnewline
\textbf{typical for 2}&&&&&&&\tabularnewline
Saxifraga stellaris ssp. robusta&hl&28&\multicolumn{1}{|l|}{85***}&.&.&73***&.\tabularnewline
Deschampsia cespitosa&ml&.&\multicolumn{1}{|l|}{85***}&.&.&.&.\tabularnewline
Epilobium alsinifolium&ml&.&\multicolumn{1}{|l|}{54***}&.&.&.&.\tabularnewline
Rhizomnium magnifolium&ml&4&\multicolumn{1}{|l|}{54***}&.&17&.&.\tabularnewline
Caltha palustris&ml&.&\multicolumn{1}{|l|}{54***}&.&.&.&.\tabularnewline
Carex nigra&ml&.&\multicolumn{1}{|l|}{46***}&.&.&.&.\tabularnewline
Cardamine amara ssp. austriaca&ml&.&\multicolumn{1}{|l|}{38***}&.&.&.&.\tabularnewline
Alchemilla monticola&ml&.&\multicolumn{1}{|l|}{31***}&.&.&.&.\tabularnewline
Carex limosa&ml&.&\multicolumn{1}{|l|}{31***}&.&.&.&.\tabularnewline
Pinguicula vulgaris&ml&.&\multicolumn{1}{|l|}{31***}&.&.&.&.\tabularnewline
&&&&&&&\tabularnewline
\textbf{typical for 3}&&&&&&&\tabularnewline
Saxifraga stellaris s.lat.&hl&.&.&\multicolumn{1}{|l|}{100***}&17&.&.\tabularnewline
Philonotis seriata&ml&.&62***&\multicolumn{1}{|l|}{100***}&.&33&.\tabularnewline
Scapania undulata&ml&.&31*&\multicolumn{1}{|l|}{67**}&17&7&.\tabularnewline
Viola biflora&hl&8&.&\multicolumn{1}{|l|}{50**}&17&.&.\tabularnewline
&&&&&&&\tabularnewline
\textbf{typical for 4}&&&&&&&\tabularnewline
Sphagnum capillifolium&ml&.&8&.&\multicolumn{1}{|l|}{100***}&.&.\tabularnewline
Pinguicula vulgaris&hl&.&.&.&\multicolumn{1}{|l|}{83***}&40**&.\tabularnewline
Swertia perennis&hl&.&8&.&\multicolumn{1}{|l|}{67***}&.&.\tabularnewline
Willemetia stipitata ssp. stipitata&hl&.&15&.&\multicolumn{1}{|l|}{67**}&40**&.\tabularnewline
Luzula alpinopilosa s.str.&hl&.&.&.&\multicolumn{1}{|l|}{67***}&.&.\tabularnewline
Potentilla erecta&hl&.&.&.&\multicolumn{1}{|l|}{67***}&13&.\tabularnewline
Aulacomnium palustre&ml&4&15&.&\multicolumn{1}{|l|}{67***}&7&.\tabularnewline
Carex flava s.lat.&hl&4&.&.&\multicolumn{1}{|l|}{50***}&.&.\tabularnewline
Drosera rotundifolia&hl&.&8&.&\multicolumn{1}{|l|}{50***}&.&.\tabularnewline
Trichophorum cespitosum ssp. cespitosum&hl&.&.&.&\multicolumn{1}{|l|}{50***}&.&.\tabularnewline
Dactylorhiza maculata s.lat.&hl&4&.&.&\multicolumn{1}{|l|}{33*}&.&.\tabularnewline
Alchemilla glabra&hl&.&.&.&\multicolumn{1}{|l|}{33**}&.&.\tabularnewline
Valeriana dioica&hl&.&.&.&\multicolumn{1}{|l|}{33**}&.&.\tabularnewline
Scorpidium scorpioides&ml&.&.&.&\multicolumn{1}{|l|}{33**}&.&.\tabularnewline
&&&&&&&\tabularnewline
\textbf{typical for 5}&&&&&&&\tabularnewline
Juncus castaneus&hl&20&.&.&17&\multicolumn{1}{|l|}{100***}&.\tabularnewline
Cardamine »rivularis«&hl&20&15&.&17&\multicolumn{1}{|l|}{87***}&.\tabularnewline
Juncus triglumis ssp. triglumis&hl&.&8&.&.&\multicolumn{1}{|l|}{80***}&41\tabularnewline
Viola palustris&hl&.&.&.&.&\multicolumn{1}{|l|}{73***}&.\tabularnewline
Agrostis stolonifera s.str.&hl&.&.&.&.&\multicolumn{1}{|l|}{60***}&.\tabularnewline
Philonotis fontana&ml&4&8&.&.&\multicolumn{1}{|l|}{47***}&.\tabularnewline
Bryum schleicheri var. schleicheri&ml&.&.&.&.&\multicolumn{1}{|l|}{47***}&.\tabularnewline
Alchemilla Sect. Coriaceae&hl&.&.&.&.&\multicolumn{1}{|l|}{33***}&.\tabularnewline
Montia fontana ssp. fontana&hl&.&.&.&.&\multicolumn{1}{|l|}{33***}&.\tabularnewline
Gentiana bavarica var. subacaulis&hl&.&.&.&.&\multicolumn{1}{|l|}{33***}&.\tabularnewline
&&&&&&&\tabularnewline
\textbf{typical for 6}&&&&&&&\tabularnewline
Carex bicolor&hl&.&.&.&.&.&\multicolumn{1}{|l|}{77***}\tabularnewline
Saxifraga aizoides&hl&.&.&.&17&7&\multicolumn{1}{|l|}{64***}\tabularnewline
Salix retusa s.str.&hl&.&.&.&.&7&\multicolumn{1}{|l|}{41***}\tabularnewline
&&&&&&&\tabularnewline
\textbf{not particular typical}&&&&&&&\tabularnewline
Deschampsia cespitosa&hl&44&.&100*&67&100***&27\tabularnewline
Epilobium alsinifolium&hl&36&.&50&33&60**&.\tabularnewline
Poa alpina&hl&24&15&50&33&33&23\tabularnewline
Eriophorum angustifolium&hl&.&23&33&83**&73***&9\tabularnewline
Caltha palustris&hl&28&.&17&50&73***&.\tabularnewline
Persicaria vivipara&hl&24&.&.&.&20&55***\tabularnewline
Carex nigra&hl&.&.&50&83**&87***&.\tabularnewline
Cardamine amara ssp. austriaca&hl&36*&.&33&17&27&.\tabularnewline
Carex echinata&hl&.&15&33&50&53***&.\tabularnewline
Saxifraga stellaris ssp. prolifera&hl&24&.&.&17&47**&.\tabularnewline
Carex frigida&hl&.&.&.&.&33*&36**\tabularnewline
Bartsia alpina&hl&.&8&.&50*&20&23\tabularnewline
Nardus stricta&hl&.&.&17&33&53***&.\tabularnewline
Parnassia palustris&hl&4&.&.&33&7&27*\tabularnewline
Stellaria alsine&hl&12&8&.&.&27*&.\tabularnewline
Sedum villosum&hl&.&8&.&17&40***&.\tabularnewline
Epilobium nutans&hl&.&23&.&.&33**&.\tabularnewline
Carex ferruginea s.str.&hl&28***&.&.&.&.&.\tabularnewline
Tofieldia calyculata&hl&8&15&.&.&13&5\tabularnewline
Festuca pulchella s.lat.&hl&8&23&.&33&.&.\tabularnewline
Equisetum variegatum&hl&.&.&.&33&.&23*\tabularnewline
Chaerophyllum villarsii&hl&24***&.&.&.&.&.\tabularnewline
Gentiana bavarica s.str.&hl&8&.&.&17&.&14\tabularnewline
Bellidiastrum michelii&hl&12&.&.&.&13&5\tabularnewline
Juncus alpinoarticulatus ssp. alpinoarticulatus&hl&4&8&.&33&7&5\tabularnewline
Carex flava var. alpina&hl&.&8&.&.&33***&.\tabularnewline
Tofieldia pusilla&hl&.&8&.&.&13&14\tabularnewline
Agrostis rupestris&hl&.&.&.&.&13&18*\tabularnewline
Saxifraga oppositifolia ssp. oppositifolia&hl&.&.&.&.&.&27***\tabularnewline
Epilobium anagallidifolium&hl&16*&8&.&.&.&.\tabularnewline
Selaginella selaginoides&hl&4&8&.&.&20*&.\tabularnewline
Carex davalliana&hl&4&8&.&33*&7&.\tabularnewline
Cerastium fontanum s.str.&hl&.&.&17&.&27**&.\tabularnewline
Carex limosa&hl&.&.&33*&50**&.&.\tabularnewline
Homogyne alpina&hl&.&.&17&17&20*&.\tabularnewline
Juncus filiformis&hl&.&.&17&17&20*&.\tabularnewline
Carex firma&hl&.&.&.&.&.&23***\tabularnewline
Carex parviflora&hl&.&.&.&.&7&18*\tabularnewline
Carex atrofusca&hl&.&.&.&.&.&23***\tabularnewline
Silene acaulis ssp. exscapa&hl&.&.&.&.&.&23***\tabularnewline
Alchemilla straminea&hl&16**&.&.&.&.&.\tabularnewline
Salix waldsteiniana&hl&8&.&.&.&.&9\tabularnewline
Dicranoweisia crispula&hl&12&.&17&.&.&.\tabularnewline
Tussilago farfara&hl&16**&.&.&.&.&.\tabularnewline
Carex dioica&hl&.&.&.&33*&13&.\tabularnewline
Kobresia simpliciuscula&hl&.&.&.&.&.&18**\tabularnewline
Luzula sudetica&hl&.&.&.&.&27***&.\tabularnewline
Campanula scheuchzeri&hl&.&.&.&.&20*&5\tabularnewline
Achillea moschata&hl&.&.&.&.&.&18**\tabularnewline
Carex capillaris&hl&.&.&.&.&.&18**\tabularnewline
Achillea atrata&hl&8&.&.&.&.&5\tabularnewline
Pinguicula alpina&hl&8&.&.&.&.&5\tabularnewline
Veronica beccabunga&hl&12*&.&.&.&.&.\tabularnewline
Heliosperma pusillum ssp. pusillum&hl&12*&.&.&.&.&.\tabularnewline
Aconitum tauricum ssp. tauricum&hl&4&15&.&.&.&.\tabularnewline
Carex pauciflora&hl&.&8&.&33*&.&.\tabularnewline
Agrostis canina s.str.&hl&.&8&.&33*&.&.\tabularnewline
Juncus articulatus&hl&.&.&.&.&20**&.\tabularnewline
Carex panicea&hl&.&.&.&.&20**&.\tabularnewline
Mutellina adonidifolia&hl&.&.&.&.&20**&.\tabularnewline
Primula minima&hl&.&.&.&.&20**&.\tabularnewline
Sesleria caerulea s.str.&hl&.&.&.&.&.&14*\tabularnewline
Salix serpyllifolia&hl&.&.&.&.&.&14*\tabularnewline
Euphrasia minima s.str.&hl&.&.&.&.&.&14*\tabularnewline
Ranunculus montanus s.str.&hl&4&.&.&.&.&5\tabularnewline
Eriophorum scheuchzeri&hl&4&.&.&17&.&.\tabularnewline
Alchemilla decumbens&hl&8&.&.&.&.&.\tabularnewline
Cystopteris fragilis s.str.&hl&8&.&.&.&.&.\tabularnewline
Myosotis palustris agg.&hl&4&.&.&17&.&.\tabularnewline
Montia fontana ssp. variabilis&hl&4&8&.&.&.&.\tabularnewline
Scorzoneroides helvetica&hl&4&.&.&.&.&5\tabularnewline
Peucedanum ostruthium&hl&4&8&.&.&.&.\tabularnewline
Taraxacum sp.&hl&.&8&.&17&.&.\tabularnewline
Alchemilla sp.&hl&.&.&17&.&7&.\tabularnewline
Anthoxanthum alpinum&hl&.&.&17&.&7&.\tabularnewline
Eleocharis quinqueflora&hl&.&.&.&17&7&.\tabularnewline
Armeria alpina&hl&.&.&.&.&.&9\tabularnewline
Arabis soyeri ssp. subcoriacea&hl&.&.&.&.&7&5\tabularnewline
Potentilla aurea&hl&.&.&.&.&13*&.\tabularnewline
Soldanella pusilla ssp. alpicola&hl&.&.&.&.&13*&.\tabularnewline
Carex oederi&hl&.&.&.&.&13*&.\tabularnewline
Festuca pseudodura&hl&.&.&.&.&13*&.\tabularnewline
Phleum commutatum&hl&.&.&.&.&13*&.\tabularnewline
Sagina saginoides&hl&.&.&.&.&13*&.\tabularnewline
Veronica alpina&hl&.&.&.&.&7&5\tabularnewline
Trifolium badium&hl&.&.&.&.&7&5\tabularnewline
Soldanella alpina&hl&.&.&.&.&13*&.\tabularnewline
Pedicularis rostratocapitata ssp. rostratocapitata&hl&.&.&.&.&.&9\tabularnewline
Salix reticulata&hl&.&.&.&.&.&9\tabularnewline
Trifolium pallescens&hl&.&.&.&.&.&9\tabularnewline
Trifolium pratense ssp. nivale&hl&.&.&.&.&.&9\tabularnewline
Carex atrata&hl&.&.&.&.&.&9\tabularnewline
Juncus jacquinii&hl&.&.&.&.&.&9\tabularnewline
Salix hastata ssp. hastata&hl&4&.&.&.&.&.\tabularnewline
Pellia epiphylla&hl&4&.&.&.&.&.\tabularnewline
Equisetum sylvaticum&hl&4&.&.&.&.&.\tabularnewline
Cirsium palustre&hl&4&.&.&.&.&.\tabularnewline
Galium palustre ssp. palustre&hl&4&.&.&.&.&.\tabularnewline
Hieracium murorum&hl&4&.&.&.&.&.\tabularnewline
Linum catharticum&hl&4&.&.&.&.&.\tabularnewline
Veronica montana&hl&.&8&.&.&.&.\tabularnewline
Geum rivale&hl&.&8&.&.&.&.\tabularnewline
Potentilla reptans&hl&.&8&.&.&.&.\tabularnewline
Fissidens adianthoides&hl&.&8&.&.&.&.\tabularnewline
Equisetum palustre&hl&.&8&.&.&.&.\tabularnewline
Viola sp.&hl&.&8&.&.&.&.\tabularnewline
Doronicum austriacum&hl&4&.&.&.&.&.\tabularnewline
Dryopteris filix-mas s.str.&hl&4&.&.&.&.&.\tabularnewline
Saxifraga rotundifolia ssp. rotundifolia&hl&4&.&.&.&.&.\tabularnewline
Valeriana tripteris&hl&4&.&.&.&.&.\tabularnewline
Diplophyllum taxifolium&hl&.&.&17&.&.&.\tabularnewline
Hypnum lindbergii&hl&.&.&17&.&.&.\tabularnewline
Racomitrium affine&hl&.&.&17&.&.&.\tabularnewline
Cephalanthera damasonium&hl&.&.&.&17&.&.\tabularnewline
Lychnis flos-cuculi&hl&.&.&.&17&.&.\tabularnewline
Allium schoenoprasum var. alpinum&hl&.&.&.&17&.&.\tabularnewline
Crepis aurea ssp. aurea&hl&.&.&.&17&.&.\tabularnewline
Sphagnum girgensohnii&hl&.&.&.&17&.&.\tabularnewline
Trichophorum alpinum&hl&.&.&.&17&.&.\tabularnewline
Triglochin palustre&hl&.&.&.&17&.&.\tabularnewline
Briza media&hl&.&.&.&.&7&.\tabularnewline
Festuca nigrescens&hl&.&.&.&.&7&.\tabularnewline
Valeriana celtica ssp. norica&hl&.&.&.&.&7&.\tabularnewline
Eriophorum vaginatum&hl&.&.&.&.&7&.\tabularnewline
Loiseleuria procumbens&hl&.&.&.&.&7&.\tabularnewline
Salix alpina&hl&.&.&.&.&7&.\tabularnewline
Calluna vulgaris&hl&.&.&.&.&7&.\tabularnewline
Arabis stellulata&hl&.&.&.&.&.&5\tabularnewline
Kobresia myosuroides&hl&.&.&.&.&.&5\tabularnewline
Agrostis alpina s.str.&hl&.&.&.&.&.&5\tabularnewline
Euphrasia salisburgensis s.str.&hl&.&.&.&.&.&5\tabularnewline
Festuca pumila&hl&.&.&.&.&.&5\tabularnewline
Gentiana prostrata&hl&.&.&.&.&.&5\tabularnewline
Linaria alpina ssp. alpina&hl&.&.&.&.&.&5\tabularnewline
Saxifraga caesia&hl&.&.&.&.&.&5\tabularnewline
Minuartia sedoides&hl&.&.&.&.&.&5\tabularnewline
Artemisia mutellina&hl&.&.&.&.&.&5\tabularnewline
Carex lachenalii&hl&.&.&.&.&.&5\tabularnewline
Cerastium uniflorum&hl&.&.&.&.&.&5\tabularnewline
Lotus corniculatus s.str.&hl&.&.&.&.&.&5\tabularnewline
Salix breviserrata&hl&.&.&.&.&.&5\tabularnewline
Gypsophila repens&hl&.&.&.&.&.&5\tabularnewline
Oxytropis halleri ssp. halleri&hl&.&.&.&.&.&5\tabularnewline
Veronica aphylla&hl&.&.&.&.&.&5\tabularnewline
Primula farinosa&hl&.&.&.&.&.&5\tabularnewline
Achillea millefolium s.str.&hl&.&.&.&.&.&5\tabularnewline
Alchemilla fissa s.str.&hl&.&.&.&.&.&5\tabularnewline
Festuca sp.&hl&.&.&.&.&.&5\tabularnewline
Leontodon hispidus s.lat.&hl&.&.&.&.&.&5\tabularnewline
Polygala alpestris ssp. alpestris&hl&.&.&.&.&.&5\tabularnewline
Prunella vulgaris&hl&.&.&.&.&.&5\tabularnewline
Ranunculus acris ssp. acris&hl&.&.&.&.&.&5\tabularnewline
Pedicularis aspleniifolia&hl&.&.&.&.&.&5\tabularnewline
Doronicum glaciale ssp. glaciale&hl&.&.&.&.&.&5\tabularnewline
Solorina bispora ssp. bispora&hl&.&.&.&.&.&5\tabularnewline
Ranunculus alpestris s.str.&hl&.&.&.&.&.&5\tabularnewline
Salix herbacea&hl&.&.&.&.&.&5\tabularnewline
Astragalus australis&hl&.&.&.&.&.&5\tabularnewline
Carex sempervirens ssp. sempervirens&hl&.&.&.&.&.&5\tabularnewline
Minuartia gerardii&hl&.&.&.&.&.&5\tabularnewline
Palustriella commutata var. falcata&ml&80**&92**&.&.&60&23\tabularnewline
Bryum pseudotriquetrum var. pseudotriquetrum&ml&60**&54&17&33&33&5\tabularnewline
Dichodontium palustre&ml&.&69***&.&50&33&.\tabularnewline
Jungermannia sp.&ml&28*&23&33&17&.&.\tabularnewline
Saxifraga aizoides&ml&24&46**&.&.&.&.\tabularnewline
Brachythecium rivulare&ml&28*&15&33&.&.&.\tabularnewline
Campylium stellatum&ml&8&15&17&33&20&.\tabularnewline
Blindia acuta&ml&.&31*&17&33&7&.\tabularnewline
Cratoneuron filicinum&ml&20*&15&.&.&.&.\tabularnewline
Palustriella decipiens&ml&24***&.&.&.&.&.\tabularnewline
Philonotis calcarea&ml&24***&.&.&.&.&.\tabularnewline
Bryum pallens agg.&ml&8&15&33&.&.&.\tabularnewline
Racomitrium aciculare&ml&4&8&33&33&.&.\tabularnewline
Jungermannia obovata&ml&4&23*&33&.&.&.\tabularnewline
Arabis soyeri ssp. subcoriacea&ml&20**&.&.&.&.&.\tabularnewline
Marchantia polymorpha s.lat.&ml&8&23*&.&.&.&.\tabularnewline
Palustriella commutata var. commutata&ml&16*&.&.&.&7&.\tabularnewline
Preissia quadrata&ml&12&.&.&.&13&.\tabularnewline
Bryum turbinatum&ml&8&15&17&.&.&.\tabularnewline
Kiaeria starkei&ml&8&8&17&17&.&.\tabularnewline
Warnstorfia exannulata&ml&.&.&33*&17&13&.\tabularnewline
Bryum sp.&ml&16**&.&.&.&.&.\tabularnewline
Dichodontium pellucidum&ml&4&.&.&17&13&.\tabularnewline
Pellia epiphylla&ml&.&23**&.&17&.&.\tabularnewline
Polytrichum alpinum&ml&4&8&.&33*&.&.\tabularnewline
Plagiothecium ruthei&ml&4&8&33*&.&.&.\tabularnewline
Diplophyllum taxifolium&ml&.&8&17&17&.&.\tabularnewline
Oncophorus virens&ml&4&15&.&.&.&.\tabularnewline
Dicranum scoparium&ml&.&15&.&17&.&.\tabularnewline
Plagiochila asplenioides&ml&4&8&.&17&.&.\tabularnewline
Warnstorfia fluitans&ml&.&.&33*&17&.&.\tabularnewline
Hygrohypnum luridum&ml&8&.&.&.&.&.\tabularnewline
Hymenostylium recurvirostrum var. recurvirostrum&ml&8&.&.&.&.&.\tabularnewline
Rhytidiadelphus squarrosus&ml&4&8&.&.&.&.\tabularnewline
Mnium marginatum&ml&4&.&.&17&.&.\tabularnewline
Lophozia ventricosa&ml&4&8&.&.&.&.\tabularnewline
Lophozia sp.&ml&4&.&.&17&.&.\tabularnewline
Tortella fragilis&ml&.&15*&.&.&.&.\tabularnewline
Ditrichum pusillum&ml&.&8&.&17&.&.\tabularnewline
Ditrichum flexicaule&ml&.&8&.&.&7&.\tabularnewline
Dicranoweisia crispula&ml&.&.&17&.&7&.\tabularnewline
Warnstorfia sarmentosa&ml&.&.&.&17&7&.\tabularnewline
Sphagnum compactum&ml&.&.&.&17&7&.\tabularnewline
Hylocomium splendens&ml&.&.&.&17&7&.\tabularnewline
Calliergonella cuspidata&ml&.&.&.&.&13*&.\tabularnewline
Scorpidium cossonii&ml&.&.&.&.&13*&.\tabularnewline
Solorina spongiosa&ml&4&.&.&.&.&.\tabularnewline
Distichium capillaceum&ml&4&.&.&.&.&.\tabularnewline
Tortella tortuosa&ml&4&.&.&.&.&.\tabularnewline
Grimmia sp.&ml&4&.&.&.&.&.\tabularnewline
Leiocolea sp.&ml&4&.&.&.&.&.\tabularnewline
Oedogonium sp.&ml&4&.&.&.&.&.\tabularnewline
Myurella julacea&ml&4&.&.&.&.&.\tabularnewline
Bryum weigelii&ml&.&8&.&.&.&.\tabularnewline
Polytrichum juniperinum&ml&.&8&.&.&.&.\tabularnewline
Ditrichum lineare&ml&.&8&.&.&.&.\tabularnewline
Harpanthus flotovianus&ml&.&8&.&.&.&.\tabularnewline
Amphidium mougeotii&ml&4&.&.&.&.&.\tabularnewline
Ceratodon purpureus&ml&.&8&.&.&.&.\tabularnewline
Lophozia excisa&ml&.&8&.&.&.&.\tabularnewline
Platyhypnidium riparioides&ml&.&8&.&.&.&.\tabularnewline
Jungermannia atrovirens&ml&.&.&17&.&.&.\tabularnewline
Leptogium lichenoides var. lichenoides&ml&.&.&17&.&.&.\tabularnewline
Racomitrium aquaticum&ml&.&.&17&.&.&.\tabularnewline
Schistidium rivulare&ml&.&.&17&.&.&.\tabularnewline
Scorpidium revolvens&ml&.&.&17&.&.&.\tabularnewline
Mnium hornum&ml&4&.&.&.&.&.\tabularnewline
Campylopus subulatus var. schimperi&ml&4&.&.&.&.&.\tabularnewline
Plagiomnium undulatum&ml&4&.&.&.&.&.\tabularnewline
Conocephalum conicum&ml&4&.&.&.&.&.\tabularnewline
Brachythecium salebrosum&ml&.&.&.&17&.&.\tabularnewline
Jungermannia hyalina&ml&.&.&.&17&.&.\tabularnewline
Sphagnum fuscum&ml&.&.&.&17&.&.\tabularnewline
Tomentypnum nitens&ml&.&.&.&17&.&.\tabularnewline
Dicranum fuscescens&ml&.&.&17&.&.&.\tabularnewline
Racomitrium affine&ml&.&.&17&.&.&.\tabularnewline
Sphagnum squarrosum&ml&.&.&17&.&.&.\tabularnewline
Anthoxanthum alpinum&ml&.&.&.&17&.&.\tabularnewline
Calypogeia azurea&ml&.&.&.&17&.&.\tabularnewline
Euphrasia sp.&ml&.&.&.&17&.&.\tabularnewline
Lophozia obtusa&ml&.&.&.&17&.&.\tabularnewline
Sphagnum girgensohnii&ml&.&.&.&17&.&.\tabularnewline
undetermined bryophyte(s)&ml&.&.&.&.&7&.\tabularnewline
Dicranum bonjeanii&ml&.&.&.&.&7&.\tabularnewline
Riccardia latifrons&ml&.&.&.&.&7&.\tabularnewline
Dicranella varia&ml&.&.&.&.&7&.\tabularnewline
Tayloria linguata&ml&.&.&.&.&7&.\tabularnewline
Atrichum undulatum&ml&.&.&.&.&7&.\tabularnewline
Sphagnum warnstorfii&ml&.&.&.&.&7&.\tabularnewline
Thamnolia vermicularis var. vermicularis&ml&.&.&.&.&.&5\tabularnewline
\bottomrule
\end{longtable}

